---
title: "Subsetting via Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Subsetting via Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vec)
```

## Functions of 1 argument

We start by defining a vector to be of the new `vec` class

```{r}
x <- as_vec(1:15)
x
```

{vec} provides some helpful vector-operation functions; `is_even(a)` and `is_odd(a)`

```{r}
is_even(6)
is_even(7)
is_odd(7)
```

These can be used in the regular way

```{r}
x[is_even(x)]
```

because this is evaluated first

```{r}
is_even(x)
```

producing the logical vector for regular subsetting.

For vectors of class `vec`, you can also specify a formula involving arguments

```{r}
x[~is_even(x)]
```

Or, if you wish to refer to the enclosing vector, you can use a `.` placeholder

```{r}
x[~is_even(.)]
```

A new syntax is introduced where a bare function can be used with the effect that
`x[f] == x[f(x)]`

```{r}
x[is_even]
x[is_odd]
```

This function can also be used to replace those values for which `is_even(x) == TRUE`

```{r}
x[is_even] <- 99
x
```

## Functions of more than 1 argument

Resetting the vector

```{r}
x <- as_vec(1:15)
x
```

{vec} also provides a two-argument function `is_divisible_by(a, b)`

```{r}
is_divisible_by(11, 5)
is_divisible_by(10, 5)
is_divisible_by(1:6, 2)
```

which can be used in the same ways, using explicit arguments

```{r}
x[is_divisible_by(x, 3)]
x[~is_divisible_by(x, 3)]
x[~is_divisible_by(., 3)]
```

again because this is evaluated first

```{r}
is_divisible_by(x, 3)
```

For multiple arguments with a bare function, one option would be to pass named
arguments to the function via `[`'s `...` argument, e.g.

```{r}
x[is_divisible_by, n = 3]
```

but this is somewhat unclean; the `b` refers to the function argument and looks
too similar to regular `[` subsetting.

Alternatively, curry the function; consume one of the arguments

```{r}
div3 <- function(aa) {
  is_divisible_by(aa, n = 3)
}

x[div3]
```

This function can also be used to replace those values for which `div3(x) == TRUE`

```{r}
x[div3] <- 99
x
```
